Fundamental measure theory for hard polyhedra.

### 2013-02-06 papers/polyhedra/paper.tex
work on generic solution for weighting functions of polyhedra Tested everything on node03.

\newcommand{\fixme}[1]{\red{[#1]}}

@@

\subsection{Ideal gas free energy}
To address this, we will
first consider the free energy of an ideal gas.
\begin{widetext}
\begin{align}
  A_{\textit{ideal}} &=
  k_BT \int
  \left(n(\rr,\rot)\ln(\Lambda^3\Theta^3 n(\rr,\rot)) - n(\rr,\rot)
  \right) d\rr d\rot
  \\
  &=
  k_BT \sum_{lmm'} \int
  n_{lmm'}(\rr)D_{lmm'}(\rot)\left(
  \ln\left(\Lambda^3\Theta^3 \sum_{l_1m_1m'_1} n_{l_1m_1m'_1}(\rr)D_{l_1m_1m'_1}(\rot)\right) - 1
  \right) d\rr d\rot
  \\
  &=
  k_BT \int n_{000}(\rr)
  \left(\ln\left(\Lambda^3\Theta^3 \sum_{lmm'} n_{lmm'}(\rr)D_{lmm'}(\rot)\right) - 1
  \right) d\rr d\rot
  \\&+
  k_BT \sum_{l>1,mm'} \int
  n_{lmm'}(\rr)D_{lmm'}(\rot)
  \ln\left(\Lambda^3\Theta^3 \sum_{l_1m_1m'_1} n_{l_1m_1m'_1}(\rr)D_{l_1m_1m'_1}(\rot)\right)
  d\rr d\rot
  \\
  &= A_{000} + \sum_{l>1,mm'} A_{lmm'} - k_BT\int n_{000}(\rr)d\rr
\end{align}
Here I have broken the $000$ term out of the outer summation over
$lmm'$, since this one is special, since it is independent of $\rot$.
We'll tackle that integral first, since it is a tad simpler.
\begin{align}
  A_{000} &= k_BT\int
  n_{000}(\rr)\ln\left(
  \sum_{lmm'} n_{lmm'}(\rr)D_{lmm'}(\rot)
  \right)
  d\rr d\rot
\end{align}
We can simplify this integral a bit if we write the log as a power
series...
\begin{align}
  A_{000}
  &= k_BT\int
  n_{000}(\rr)\ln\left(
  n_{000}(\rr)\left(1 + \frac{\sum_{lmm'} n_{lmm'}(\rr)D_{lmm'}(\rot)}{n_{000}(\rr)}\right)
  \right)
  d\rr d\rot
  \\
  &= k_BT\int
  n_{000}(\rr)\ln n_{000}(\rr)
  \\&+k_BT\int
  n_{000}(\rr)\ln\left(1 + \frac{\sum_{lmm'} n_{lmm'}(\rr)D_{lmm'}(\rot)}{n_{000}(\rr)}\right)
  d\rr d\rot
  \\
  &= k_BT\int
  n_{000}(\rr)\ln n_{000}(\rr)
  \\&+k_BT\int
  n_{000}(\rr)\left(\frac{\sum_{lmm'} n_{lmm'}(\rr)D_{lmm'}(\rot)}{n_{000}(\rr)}\right)
  d\rr d\rot
  \\&-\frac{k_BT}{2!}\int
  n_{000}(\rr)\left(\frac{\sum_{lmm'} n_{lmm'}(\rr)D_{lmm'}(\rot)}{n_{000}(\rr)}\right)^2
  d\rr d\rot
  \\&+\cdots
\end{align}
Now the linear term in the power series will vanish, since the
summation is over $l>0$ only.  In the quadratic term, only a few terms
will survive, and we'll end up with
\begin{align}
  A_{000}
  &=
  k_BT\int
  n_{000}(\rr)\ln n_{000}(\rr)d\rr
  \\&\quad-\frac{k_BT}{2!}\int
  \frac{\sum_{lmm'} \frac{2l+1}{8\pi^2} n_{lmm'}(\rr)n_{l,-m,-m'}}{n_{000}(\rr)}
  d\rr
  \\&\quad+\cdots
  \\
  &=
  k_BT\int
  n_{000}(\rr)\ln n_{000}(\rr)d\rr
  \\&\quad-\frac{k_BT}{2!}\int
  \frac{\sum_{lmm'} \frac{2l+1}{8\pi^2} |n_{lmm'}(\rr)|^2}{n_{000}(\rr)}
  d\rr
  \\&\quad+\cdots
\end{align}
Now an interesting question is whether we can mimic this power series
with a log, such as
\begin{align}
  A_{000}
  &=
  k_BT\int
  n_{000}(\rr)\ln \left( \sqrt{n_{000}(\rr)^2 + \sum_{lmm'}
    c_ln_{lmm'}(\rr)^2} \right)d\rr
  \\
  &= 
  k_BT\int
  n_{000}(\rr)\ln n_{000}(\rr)d\rr
  \\&\quad+
  k_BT\int n_{000}(\rr)\ln\left( \sqrt{1 + \frac{\sum_{lmm'}
    c_ln_{lmm'}(\rr)^2}{n_{000}(\rr)^2}} \right)d\rr
  \\
  &=
  k_BT\int
  n_{000}(\rr)\ln n_{000}(\rr)d\rr
  \\&\quad+
  k_BT\int \frac12 \frac{\sum_{lmm'}
    c_ln_{lmm'}(\rr)^2}{n_{000}(\rr)} d\rr
  \\&\quad+\cdots
\end{align}
from which we can conclude that to get an answer correct to the
quadratic order, we need
\begin{align}
  c_l &= -\frac{2l+1}{8\pi^2}
\end{align}
which seems all right except for the sign:  I expect that the free
energy should increase as we increase $n_{lmm'}$, since it means the
system is becoming more ordered, and it looks like to this quadratic
term, the free energy decreases... except that we're only looking at
$A_{000}$ right now, and thus are neglecting a possibly significant
increase due to the other terms...  so perhaps we should call this all
right, and move on for now.

@@

\end{widetext}
\subsection{Finding the orientational moments}
We find the orientational moments $n_{lmm'}(\rr)$ by minimizing the
free energy.  Let's begin by optimizing the free energy with respect
to nonzero angular momenta:
\begin{align}
  0&=\frac{\delta A}{\delta n_{lmm'}(\rr)} \\
  &= \frac{2l+1}{8\pi^2}n_{lmm'}(\rr)
  + k_BT \int\sum_\alpha
  \frac{\partial \Phi(\rr')}{\partial n_\alpha(\rr')}
  \frac{\delta n_\alpha(\rr')}{\delta n_{lmm'}(\rr)} d\rr'
  \\
  &=
   \frac{2l+1}{8\pi^2}n_{lmm'}(\rr)
  \\&\quad+ k_BT \int\sum_\alpha
  \frac{\partial \Phi(\rr')}{\partial n_\alpha(\rr')}
  \tilde{w}_\alpha^{lm}(|\rr-\rr'|)Y_{lm'}(\widehat{\rr-\rr'}) d\rr'
\end{align}
Solving for $n_{lmm'}(\rr)$, we find that
\begin{align}\label{eq:nlmm'}
  n_{lmm'}(\rr) &= \frac{8\pi^2k_BT}{2l+1}
  \int\sum_\alpha
  \frac{\partial \Phi(\rr')}{\partial n_\alpha(\rr')}
  \tilde{w}_\alpha^{lm}(|\rr-\rr'|)Y_{lm'}(\widehat{\rr-\rr'}) d\rr'
\end{align}
I note that this equation for $n_{lmm'}$ is approximate, since we made
an approximation when we neglected higher order terms in the expansion
of the log in the ideal gas free energy.  Thus in cases where there is
relatively little orientational ordering, it ought to be an accurate
equation.  In any case I imagine it will be plausible.

@@

\subsection{Finding the weighted densities}

\newcommand\xhat{\mathbf{\hat{x}}}
\newcommand\yhat{\mathbf{\hat{y}}}
\newcommand\zhat{\mathbf{\hat{z}}}
\newcommand\facehat{\mathbf{\hat{f}}}
\newcommand\Rface{\ensuremath{R_{\text{face}}}}
\newcommand\Rvertex{\ensuremath{R_{\text{vertex}}}}

Here I will discuss how to find the weighted densities we need in
order to study polyhedra.  We begin with $n_3(\rr)$, the packing
fraction.
\begin{align}
  w_3(\rr) &= 1 \text{ inside the polyhedron}\\
  &= 0 \text{ outside the polyhedron} \\
  &= \prod_i^{\text{faces}} \Theta(\Rface - \rr\cdot\facehat_i)
\end{align}
This is pretty easy, although the integrals will be less so.  The
$000$ integral is always going to give us something that is
essentially the same, but I won't go into this yet.

$n_2(\rr)$ is the area, which we can easily get from the above
weighted density.
\begin{align}
  w_2(\rr) &= |\nabla w_3(\rr)| \\
  &= \sum_i^{\text{faces}} \delta(\Rface-\rr\cdot\facehat_i)
  \prod_{j\ne i} \Theta(\Rface-\rr\cdot\facehat_j)
\end{align}
We could also just ask what the area is at a given position.

$n_1(\rr)$ is the first fundamental measure that is interestingly
different for polyhedra than it is for spheres.  This is a measure of
the mean curvature, and polyhedra have no curvature except at the
edges.  Thus $n_1(\rr)$ is going to be nonzero only on the edges, and
there it will be a delta function.
\begin{align}\label{eq:w1}
  w_1(\rr) &= \sum_{ij}^{\text{NN faces}}
  \Theta\left(\Rvertex - r\right)
  \delta(\Rface - \rr\cdot \facehat_i)
  \delta(\Rface - \rr\cdot \facehat_j)
\end{align}
where $\facehat_i$ is a unit vector in the direction of the $i$ face
of the polyhedron, $\Rvertex$ is the distance between the center of
the polyhedron and the vertex, and $\Rface$ is the distance of the
center of the face from the origin.  WARNING: I may have something off
in these formulas, but the general idea is there.  To find a constant
factor, we'd consider the

$n_0(\rr)$ is the fundamental measure of gaussian curvature, which is
the product of the curvature in the two eigendirections.  This is zero
(for polyhedra) except at the corners, so $n_0(\rr)$ itself is going
to be zero except at the corners.  Also, the gaussian curvature
must satisfy a sum rule, which tells us that
\begin{align}
  w_0(\rr) &= \frac1{N}\sum_{i}^{N\text{ vertices}} \delta(\rr-\rr_i)
\end{align}
Interestingly, this meas that
\begin{align}
  w_0^{000}(\rr) &= \frac{\delta(\Rvertex - |\rr|)}{4\pi \Rvertex^2}
\end{align}
which means that as far as $w_0^{000}$ is concerned, the polyhedron is a
sphere with a radius equal to the vertex distance (i.e. the distance
from the center to the vertex of the polyhedron).

>>>>

\newcommand{\todo}[1]{\textcolor{red}{[TODO: #1]}}

@@

\subsection{Ideal gas free energy}
To address this, we will
first consider the free energy of an ideal gas.
\begin{widetext}
\begin{align}
  A_{\textit{ideal}} &=
  k_BT \int
  \left(n(\rr,\rot)\ln(\Lambda^3\Theta^3 n(\rr,\rot)) - n(\rr,\rot)
  \right) d\rr d\rot \label{eq:Aideal}
  \\
  &=
  k_BT \sum_{lmm'} \int
  n_{lmm'}(\rr)D_{lmm'}(\rot)\left(
  \ln\left(\Lambda^3\Theta^3 \sum_{l_1m_1m'_1} n_{l_1m_1m'_1}(\rr)D_{l_1m_1m'_1}(\rot)\right) - 1
  \right) d\rr d\rot
  \\
  &=
  k_BT \int n_{000}(\rr)
  \left(\ln\left(\Lambda^3\Theta^3 \sum_{lmm'} n_{lmm'}(\rr)D_{lmm'}(\rot)\right) - 1
  \right) d\rr d\rot
  \\&+
  k_BT \sum_{l>1,mm'} \int
  n_{lmm'}(\rr)D_{lmm'}(\rot)
  \ln\left(\Lambda^3\Theta^3 \sum_{l_1m_1m'_1} n_{l_1m_1m'_1}(\rr)D_{l_1m_1m'_1}(\rot)\right)
  d\rr d\rot
  \\
  &= A_{000} + \sum_{l>1,mm'} A_{lmm'} - k_BT\int n_{000}(\rr)d\rr
\end{align}
Here I have broken the $000$ term out of the outer summation over
$lmm'$, since this one is special, since it is independent of $\rot$.
We'll tackle that integral first, since it is a tad simpler.
\begin{align}
  A_{000} &= k_BT\int
  n_{000}(\rr)\ln\left(
  \sum_{lmm'} n_{lmm'}(\rr)D_{lmm'}(\rot)
  \right)
  d\rr d\rot
\end{align}
We can simplify this integral a bit if we write the log as a power
series...
\begin{align}
  A_{000}
  &= k_BT\int
  n_{000}(\rr)\ln\left(
  n_{000}(\rr)\left(1 + \frac{\sum_{lmm'} n_{lmm'}(\rr)D_{lmm'}(\rot)}{n_{000}(\rr)}\right)
  \right)
  d\rr d\rot
  \\
  &= k_BT\int
  n_{000}(\rr)\ln n_{000}(\rr)
  \\&+k_BT\int
  n_{000}(\rr)\ln\left(1 + \frac{\sum_{lmm'} n_{lmm'}(\rr)D_{lmm'}(\rot)}{n_{000}(\rr)}\right)
  d\rr d\rot
  \\
  &= k_BT\int
  n_{000}(\rr)\ln n_{000}(\rr)
  \\&+k_BT\int
  n_{000}(\rr)\left(\frac{\sum_{lmm'} n_{lmm'}(\rr)D_{lmm'}(\rot)}{n_{000}(\rr)}\right)
  d\rr d\rot
  \\&-\frac{k_BT}{2!}\int
  n_{000}(\rr)\left(\frac{\sum_{lmm'} n_{lmm'}(\rr)D_{lmm'}(\rot)}{n_{000}(\rr)}\right)^2
  d\rr d\rot
  \\&+\cdots
\end{align}
Now the linear term in the power series will vanish, since the
summation is over $l>0$ only.  In the quadratic term, only a few terms
will survive, and we'll end up with
\begin{align}
  A_{000}
  &=
  k_BT\int
  n_{000}(\rr)\ln n_{000}(\rr)d\rr
  \\&\quad-\frac{k_BT}{2!}\int
  \frac{\sum_{lmm'} \frac{2l+1}{8\pi^2} n_{lmm'}(\rr)n_{l,-m,-m'}}{n_{000}(\rr)}
  d\rr
  \\&\quad+\cdots
  \\
  &=
  k_BT\int
  n_{000}(\rr)\ln n_{000}(\rr)d\rr
  \\&\quad-\frac{k_BT}{2!}\int
  \frac{\sum_{lmm'} \frac{2l+1}{8\pi^2} |n_{lmm'}(\rr)|^2}{n_{000}(\rr)}
  d\rr
  \\&\quad+\cdots
\end{align}
Now an interesting question is whether we can mimic this power series
with a log, such as
\begin{align}
  A_{000}
  &=
  k_BT\int
  n_{000}(\rr)\ln \left( \sqrt{n_{000}(\rr)^2 + \sum_{lmm'}
    c_ln_{lmm'}(\rr)^2} \right)d\rr
  \\
  &= 
  k_BT\int
  n_{000}(\rr)\ln n_{000}(\rr)d\rr
  \\&\quad+
  k_BT\int n_{000}(\rr)\ln\left( \sqrt{1 + \frac{\sum_{lmm'}
    c_ln_{lmm'}(\rr)^2}{n_{000}(\rr)^2}} \right)d\rr
  \\
  &=
  k_BT\int
  n_{000}(\rr)\ln n_{000}(\rr)d\rr
  \\&\quad+
  k_BT\int \frac12 \frac{\sum_{lmm'}
    c_ln_{lmm'}(\rr)^2}{n_{000}(\rr)} d\rr
  \\&\quad+\cdots
\end{align}
from which we can conclude that to get an answer correct to the
quadratic order, we need
\begin{align}
  c_l &= -\frac{2l+1}{8\pi^2}
\end{align}
which seems all right except for the sign:  I expect that the free
energy should increase as we increase $n_{lmm'}$, since it means the
system is becoming more ordered, and it looks like to this quadratic
term, the free energy decreases... except that we're only looking at
$A_{000}$ right now, and thus are neglecting a possibly significant
increase due to the other terms...  so perhaps we should call this all
right, and move on for now.

@@

\end{widetext}
\subsection{Finding the orientational moments}
We find the orientational moments $n_{lmm'}(\rr)$ by minimizing the
free energy.  Let's begin by optimizing the free energy with respect
to nonzero angular momenta:
\begin{align}
  0&=\frac{\delta A}{\delta n_{lmm'}(\rr)} \\
  &= \frac{2l+1}{8\pi^2}n_{lmm'}(\rr)
  + k_BT \int\sum_\alpha
  \frac{\partial \Phi(\rr')}{\partial n_\alpha(\rr')}
  \frac{\delta n_\alpha(\rr')}{\delta n_{lmm'}(\rr)} d\rr'
  \\
  &=
   \frac{2l+1}{8\pi^2}n_{lmm'}(\rr)
  \\&\quad+ k_BT \int\sum_\alpha
  \frac{\partial \Phi(\rr')}{\partial n_\alpha(\rr')}
  \tilde{w}_\alpha^{lm}(|\rr-\rr'|)Y_{lm'}(\widehat{\rr-\rr'}) d\rr'
\end{align}
Solving for $n_{lmm'}(\rr)$, we find that
\begin{align}\label{eq:nlmm'}
  n_{lmm'}(\rr) &= \frac{8\pi^2k_BT}{2l+1}
  \int\sum_\alpha
  \frac{\partial \Phi(\rr')}{\partial n_\alpha(\rr')}
  \tilde{w}_\alpha^{lm}(|\rr-\rr'|)Y_{lm'}(\widehat{\rr-\rr'}) d\rr'
\end{align}
I note that this equation for $n_{lmm'}$ is approximate, since we made
an approximation when we neglected higher order terms in the expansion
of the log in the ideal gas free energy.  Thus in cases where there is
relatively little orientational ordering, it ought to be an accurate
equation.

In cases where $n_{lmm'} \approx n_{000}$, we could reasonbly become
concerned that $n(\rr, \rot)$ could become negative for some
orientations, which would be unphysical.  If this becomes a problem,
we would want to address it by including nonlinear effects of the
$\ln$ in Equation~\ref{eq:Aideal}.  For now, let's stick with the
linear approximation, and hope for the best.  If we find that
$n_{lmm'} > n_{000}$ in practice, we would want to revisit this decision.

@@

\subsection{Finding the $000$ weighting functions for any polyhedron}

\newcommand\xhat{\mathbf{\hat{x}}}
\newcommand\yhat{\mathbf{\hat{y}}}
\newcommand\zhat{\mathbf{\hat{z}}}
\newcommand\facehat{\mathbf{\hat{f}}}
\newcommand\Rface{\ensuremath{R_f}}
\newcommand\Rvertex{\ensuremath{R_v}}

Here I will discuss how to find the weighted densities we need in
order to study polyhedra.  I will attempt in this section to evaluate
the $000$ weighting function for an arbitrary polyhedron, specified in
terms of the locations of its vertices and face centers (and possibly
also edge centers, although they should be computable from the vertex
and face radii).

\subsubsection{$w_3$}
We begin with the packing fraction $n_3(\rr)$.
\begin{align}
  w_3(\rr) &= 1 \text{ inside the polyhedron}\\
  &= 0 \text{ outside the polyhedron} \\
  &= \prod_i^{\text{faces}} \Theta(\Rface - \rr\cdot\facehat_i)
\end{align}
This is pretty easy, although the integrals will be less so.  The
$000$ integral is always going to give us something that is
essentially the same.  This integral is simply:
\begin{align}
  w_3^{000}(r) = \int w_3(\rr') \delta(|\rr'|-r) d^3r'\label{eq:w3000}
\end{align}
or we could write it as an integral over solid angle:
\begin{align}
  w_3^{000}(r) = \int w_3(\rr) d\Omega
\end{align}
Let's suppose we have $N$ faces and $M$ vertices per face.  If the
face center is at radius $\Rface$ and the vertex is at radius $\Rvertex$, then
we can compute $w_3^{000}$ by integrating over the irregular
tetrahedron enclosed by the for radii given by one vertex, one edge
center and one face center, as depicted in Figure~\ref{fig:r3000}, and
multiplying by $NM$ to account for the entire volume.  By doing this,
we can solve once for $w_3^{000}(r)$ for any regular polyhedron.

\begin{figure}
\includegraphics[width=\columnwidth]{figs/w3-000}
\caption{How we integrate for arbitrary polyhedron.}\label{fig:r3000}
\end{figure}

To begin, we solve for the positions of the vertices, which are shown
in Figure~\ref{fig:r3000}.  To perform our integration, as in
Equation~\ref{eq:w3000}, we will choose a coordinate system in which
the center of the face is in the $\xhat$ direction, and the line from the
center of the face to the center of the edge is in the $\yhat$
direction.  Our integral then becomes:
\begin{widetext}
\begin{align}
  w_3^{000}(r) &= \int w_3(\rr') \delta(|\rr'|-r) d^3r'
  \\
  &= NM \int_0^{\Rface} dx
  \int_0^{\sqrt{\Rvertex^2-\Rface^2}\cos\left(\frac{2\pi}{M}\right)} dy
  \int_0^{y\tan\left(\frac{2\pi}{M}\right)} dz \delta(r - \sqrt{x^2 +
    y^2 + z^2})
\end{align}
\end{widetext}
This integral gives a piecewise smooth result, with different forms
when $r<\Rface$, $\Rface<r<R_e$, $R_e<r<\Rvertex$ and $\Rvertex<r$ (when it is zero).

\todo{Do the above integral}

\subsubsection{$w_2$}
$n_2(\rr)$ is the area, which we can easily get from the above
weighted density.
\begin{align}
  w_2(\rr) &= |\nabla w_3(\rr)| \\
  &= \sum_i^{\text{faces}} \delta(\Rface-\rr\cdot\facehat_i)
  \prod_{j\ne i} \Theta(\Rface-\rr\cdot\facehat_j)
\end{align}
Using the same notation as in the previous section, the integral
for $w_2^{000}$ becomes:
\begin{widetext}
\begin{align}
  w_2^{000}(r) &= \int w_2(\rr') \delta(|\rr'|-r) d^3r'
  \\
  &= NM
  \int_0^{\sqrt{\Rvertex^2-\Rface^2}\cos\left(\frac{2\pi}{M}\right)} dy
  \int_0^{y\tan\left(\frac{2\pi}{M}\right)} dz \delta(r - \sqrt{\Rface^2 +
    y^2 + z^2})
\end{align}
\end{widetext}
This integral gives a piecewise smooth result, with different forms
when $r<\Rface$ (it is zero), $\Rface<r<R_e$, $R_e<r<\Rvertex$ and $\Rvertex<r$ (it is
zero).

\todo{Do the above integral}

\subsubsection{$w_1$}

$n_1(\rr)$ is the first fundamental measure that is interestingly
different for polyhedra than it is for spheres.  This is a measure of
the mean curvature, and polyhedra have no curvature except at the
edges.  Thus $n_1(\rr)$ is going to be nonzero only on the edges, and
there it will be a delta function.
\begin{align}\label{eq:w1}
  w_1(\rr) &= \sum_{ij}^{\text{NN faces}}
  \Theta\left(\Rvertex - r\right)
  \delta(\Rface - \rr\cdot \facehat_i)
  \delta(\Rface - \rr\cdot \facehat_j)
\end{align}
where $\facehat_i$ is a unit vector in the direction of the $i$ face
of the polyhedron, $\Rvertex$ is the distance between the center of
the polyhedron and the vertex, and $\Rface$ is the distance of the
center of the face from the origin.  \todo{WARNING: I may have something off
in these formulas, but the general idea is there.  To check on a
constant factor that may be off, we could check that the result
approaches the spherical value for a dodecahedron.  If it's off, it's
likely off by a largish factor.}

As before, we should be able to do this integral for $w_1^{000}$
independently of the specific polyhedron in question.  Our choice of
coordinates will be different, as we only want to integrate over the
edge, so we may as well put the edge center on the $\xhat$ axis, and
the edge itself along the $\yhat$ axis.
\begin{align}
  w_1^{000}(r) &= \int w_1(\rr') \delta(|\rr'|-r) d^3r'
  \\
  &= NM \text{constant factor}
  \int_0^{\sqrt{\Rvertex^2-\Rface^2}\sin\left(\frac{2\pi}{M}\right)} dy
  \delta(r - \sqrt{R_e^2 + y^2})
\end{align}
The only tricky bit is to get this constant factor right, which will
relate to the angle between adjacent faces.

\todo{Do this integral}

\todo{Find the constant factor}

\subsubsection{$w_0$}

$n_0(\rr)$ is the fundamental measure of gaussian curvature, which is
the product of the curvature in the two eigendirections.  This is zero
(for polyhedra) except at the corners, so $n_0(\rr)$ itself is going
to be zero except at the corners.  Also, the gaussian curvature
must satisfy a sum rule, which tells us that
\begin{align}
  w_0(\rr) &= \frac1{N}\sum_{i}^{N\text{ vertices}} \delta(\rr-\rr_i)
\end{align}
Interestingly, this means that
\begin{align}
  w_0^{000}(\rr) &= \frac{\delta(\Rvertex - |\rr|)}{4\pi \Rvertex^2}
\end{align}
which means that as far as $w_0^{000}$ is concerned, the polyhedron is a
sphere with a radius equal to the vertex distance (i.e. the distance
from the center to the vertex of the polyhedron).

\subsubsection{$\mathbf{w_{2V}}$}

\todo{TODO}

\subsubsection{$\mathbf{w_{1V}}$}

\todo{TODO}
